A studyforrest extension, an annotation of spoken language in the German dubbed movie ``Forrest Gump'' and its audio-description

### 2020-06-28 paper/main.tex
little changes on conclusions

\section*{Conclusions}
% what the paper is about
As an extension of the studyforrest dataset, we present an annotation of spoken
language in the two hours lasting ``research cut'' of the audio-visual movie
``Forrest Gump'' and its temporally aligned audio-description.
% what we did
We annotated the onset and offset of sentences, words and phonemes, and the
corresponding speaker's identity.
% what for
An additional tagging of each word's linguistic features enable independent
working groups to create sophisticated models of hemodynamic activity
correlating with linguistics aspects like phonology, grammar, syntax, and
semantics occurring in two naturalistic stimuli.
% results
Results of our dataset validating analysis that we run as a proof of concept
show that the annotation's content can indeed / in principle be used to
isolate/track speech-related networks in the human brain under life-like
conditions.

>>>>

\section*{Conclusions}
% what the paper is about
As an extension of the studyforrest dataset, we present an annotation of spoken
language in the two hours lasting ``research cut'' of the audio-visual movie
``Forrest Gump'' and its temporally aligned audio-description.
% what we did
We annotated the onset and offset of sentences, words and phonemes, and the
corresponding speaker's identity.
% what for
An additional tagging of each word's linguistic features enables independent
working groups to create sophisticated models of hemodynamic activity
correlating with linguistics aspects like phonetics, grammar, syntax, and
semantics occurring in two naturalistic stimuli.
% results
Results of our dataset validating analysis that we run as a proof of concept
show that the annotation's content can indeed / in principle be used to
isolate/track speech-related networks in the human brain under life-like
conditions.
